\setlinespacing{1.1}


\chapter{Introduction and Background} 
The field of artificial intelligence and machine learning has become exponentially prominent in recent years.
From business to social media, machine learning algorithms are being used to change the definition of efficiency and user experience.
For example, machine learning algorithms are utilised by many large companies optimize the experience with image and voice recognition and photo searching \citep{adit}. Companies such as Tesla Motors use computer vision for their self-driving automobiles, video sharing sites such as Youtube use machine learning to optimize the users preferred recommended videos and in some cases, it is even used in by medical companies for detecting cancer in patients. For example, convolutioanl neural networks (CNN's) have been used by researchers for brain tumor segmentation \citep{DBLP}. The use of CNN's proved to be an appropriate method for tumour segmentation as the results can be given from a range of 25 seconds to 3 minutes \citep{DBLP}. Artificial neural networks have been used by radiologists for Computer-Aided detections systems (CADe) and Computer-aided Diagnosis systems (CADx) to improve the accuracy of diagnoses, early detections and to minimize the time spent on evaluation by doctors \citep{CADe}. Many businesses even depend on artificial neural networks for their business model as they can be applied to many industries and disciplines. According to \citet{geocities}
artificial neural networks are used in a range of business applications such as forecasting of sales, classification of spending patterns, market targeting, risk analysis and bankruptcy prediction, to name a few. \\
Thus, considering the benefits and implications that these approaches have, the proposed project aims to illustrate how artificial neural networks work, with the use case of performing facial sentiment analysis for a retail environment. This paper is made of several chapters covering the literature of the field of neural networks, an analysis chapter which will delve into the background and high level specifications of the project and a system design and implementation. Furthermore, testing an evaluation results will be covered and a discussion about the overall project and work carried out.